Analysis of split plot design using lme4

### 2017-08-03 lme4_analysis.Rmd
Clean up summary output of lmer

```{r 2015_TShB_incidence}
library(lme4)
library(lsmeans)
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
summary(TShB_inc_AUDPS)

@@

```{r 2015_TShB_severity}
TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
summary(TShB_sev_AUDPS)

@@

```{r 2015_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
summary(LShB_sev_AUDPS)

@@

```{r 2016_TShB_incidence}
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
summary(TShB_inc_AUDPS)

@@

```{r 2016_TShB_severity}
TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
summary(TShB_sev_AUDPS)

@@

```{r 2016_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
summary(LShB_sev_AUDPS)

@@

The `lme4` `lmer` models do not appear to be a good fit based on the qqplots.
However, they do seem to agree with the `MCMCglmm` analysis results. But I'm
dubious about using these models based on the diagnostics that I see above.

>>>>

```{r 2015_TShB_incidence}
library(lme4)
library(lsmeans)
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
print(summary(TShB_inc_AUDPS), correlation = FALSE)

@@

```{r 2015_TShB_severity}
TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
print(summary(TShB_sev_AUDPS), correlation = FALSE)

@@

```{r 2015_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
print(summary(LShB_sev_AUDPS), correlation = FALSE)

@@

```{r 2016_TShB_incidence}
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
print(summary(TShB_inc_AUDPS), correlation = FALSE)

@@

```{r 2016_TShB_severity}
TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
print(summary(TShB_sev_AUDPS), correlation = FALSE)

@@

```{r 2016_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
print(summary(LShB_sev_AUDPS), correlation = FALSE)

@@
